Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-18 doc/manuscript/manuscript.Rmd
Add conclusions

eh.

@@

<!-- Conceptualization: SEE. -->
<!-- Formal analysis: BSA SEE. -->
<!-- Funding acquisition: SEE. -->
<!-- Investigation: BSA. -->
<!-- Resources: SEE. -->
<!-- Supervision: BSA. -->
<!-- Visualization: BSA SEE. -->
<!-- Writing – original draft: BSA. -->
<!-- Writing – review & editing: SEE. -->

>>>>

This study represents the largest genetic analysis of *S. sclerotiorum* from the USA to date, giving us a unique insight to continent-wide population structure and relationships between phenotypic and genotypic variables.
Based on our analysis of the relationships between MCG and MLG, we found no clear evidence that the two are directly related, suggesting that MCG do not necessarily represent vegetative compatibility groups and thus should not be used as a proxy for identifying clones. 
Populations in wmn appear to show no significant differentiation when compared to their production field counterparts, suggesting that the wmn populations of *S. sclerotiorum* may be considered representative of the surrounding regions. 
While we found no direct relationship between genotype and severity, it is evident that there is a gradient of severity by region, further supporting the need for screening in multiple locations.

@@

<!-- Conceptualization: SEE. -->
<!-- Formal analysis: BSA SEE. -->
<!-- Funding acquisition: SEE. -->
<!-- Investigation: BSA. -->
<!-- Resources: SEE. -->
<!-- Supervision: BSA. -->
<!-- Visualization: BSA SEE. -->
<!-- Writing - original draft: BSA. -->
<!-- Writing - review & editing: SEE. -->
